---
title: "CellNet with Bioconductor network and activity objects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CellNet with Bioconductor network and activity objects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Compile once, perturb many times

```{r, eval=FALSE}
library(cellnetR)
network <- cellnet_from_omnipath(OmnipathR::import_all_interactions())
compiled <- cellnet_compile(network)
screen <- perturb_batch(compiled, c("BRAF", "MAP2K1", "MAPK1"), effect = -1)
```

Imported source, reference, mechanism, confidence, and original identifiers are
retained in the R-side provenance table. Identifier mapping is an explicit
preprocessing step; CellNet does not silently translate identifiers.

## Inferred networks

```{r, eval=FALSE}
net <- cellnet_from_carnival(carnival_result)
drug_screen <- perturb_batch(cellnet_compile(net), drug_targets, effect = -1)
```

CARNIVAL supplies inferred topology. CellNet executes the supplied signed
network; it does not repeat network inference or optimize against observations.

## Omics and activity context

```{r, eval=FALSE}
activity <- decoupleR_result
compiled <- cellnet_compile(network)
set_activity_context(compiled, activity, condition = "treated")
```

Activity inference output is treated as a nonnegative context multiplier, not
new topology. For `SummarizedExperiment` or `SingleCellExperiment`, select one
sample/cell with `cellnet_context()` first. Scale interpretation remains the
caller’s responsibility.

## Pathway cone

```{r, eval=FALSE}
pathway_net <- cellnet_from_graphite(pathway_edges, sign = 1)
causal_cone(pathway_net, "EGFR")
```

Unsigned pathway relations require an explicit sign mapping before execution.
